|

### 2016-06-17 manuscript/manuscript_wtc3.Rmd
cleaning repo

\
Before seedlings were planted into each chamber they were maintained under well-watered conditions in 25 L pots and kept inside each chamber. This allowed for seedlings to gain sufficient size before planting while also allowing them to acclimate to chamber temperature treatments. Seedlings were planted into each chamber after mean seedling height reached ca. 100 cm. The top soils at this site, used in both pots and chambers, are an alluvial formation of low-fertility sandy loam soils (380 and 108 mg kg-1 total N and phosphorus respectively) with low organic matter (0.7 %) and low water holding capacity. A root exclusion barrier extended from chamber walls to the hard layer (ca. 1 m) and roots were allowed to grow freely below the barrier. Leaf gas exchange measurements were initiated in October 2013 when trees had both ample height growth and canopy development for realistic canopy light gradients to be measured. At this point, trees under AT treatment had a mean diameter of 28.2&pm;1.1 mm, height of 348&pm;15.1 cm and an leaf area of 3.9&pm;0.1 m^2^. For ET treatments, trees had a mean diameter of 34.1&pm;2.1 mm, height of 418.3&pm;23.1 cm and an leaf area of 6.2&pm;0.2 m^2^. Leaf area was calculated based on complete leaf counts and mean leaf size from a subsample.

>>>>

\
Before seedlings were planted into each chamber they were maintained under well-watered conditions in 25 L pots and kept inside each chamber. This allowed for seedlings to gain sufficient size before planting while also allowing them to acclimate to chamber temperature treatments. Seedlings were planted into each chamber after mean seedling height reached ca. 100 cm. The top soils at this site, used in both pots and chambers, are an alluvial formation of low-fertility sandy loam soils (380 and 108 mg kg-1 total N and phosphorus respectively) with low organic matter (0.7 %) and low water holding capacity. A root exclusion barrier extended from chamber walls to the hard layer (ca. 1 m) and roots were allowed to grow freely below the barrier. Leaf gas exchange measurements were initiated in October 2013 when trees had both ample height growth and canopy development for realistic canopy light gradients to be measured. At this point, trees under AT treatment had a mean diameter of 28.2&pm;1.1 mm, height of 348&pm;15.1 cm and a leaf area of 3.9&pm;0.1 m^2^. For ET treatments, trees had a mean diameter of 34.1&pm;2.1 mm, height of 418.3&pm;23.1 cm and a leaf area of 6.2&pm;0.2 m^2^. Leaf area was calculated based on complete leaf counts and mean leaf size from a subsample.
